Late Fusion via Subspace Search with Consistency Preservation

### 2017-02-28 Fusion-cvpr2017-RebuttalKit/egrebuttal-fusion.tex

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multirow}

\def\dxyred{\textcolor{red}}
\def\bE{\bf{E}}
\def\bL{\bf{L}}
\def\bX{\bf{X}}
\def\calL{\mathcal{L}}
\def\blambda{\mbox{{\boldmath $\lambda$}}}

\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{3651} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Late Fusion via Subspace Search with Consistency Preservation}

\maketitle
\thispagestyle{empty}

We thank all the reviewers.
%R3 is positive.
%R1 has some suggestions about technical analysis.
%R2 may have some misunderstandings about our paper.
We will take the comments seriously and will carefully revise the paper.
Code will be released.

\noindent\emph{\textbf{To Assigned Reviewer 1}}

{\bf Q1: The technical part in Sec 3.2 a little over-sold.}

{\bf A1:}
\textbf{Thanks for the comments.}
First, ALM is usually used for solving convex problems~[50] and (G. Liu etal, TPAMI 2013),
but our Problem~(2) is \textbf{non-convex},
and thus the convergence behavior of Algorithm 1 is unclear using standard ALM.
Second, we explicitly indicate the connection between the definition (Eq.8) and the computation (Algorithm 2) of Riemannian gradient by presenting Lemma 1,
which has never been discussed in previous works.
Third, we present every step of Algorithm~1 to make the paper self-contained.
To address the concerns, we will add more references (including G. Liu etal, TPAMI 2013) and explain the difference between our paper and the related works.

Typos will be corrected.

\noindent\emph{\textbf{To Assigned Reviewer 2}}

\textbf{Thanks for constructive comments and suggestions.}
We may have not clearly presented our method so that reviewer have misunderstood some points.
Below we mainly clarify reviewer's misunderstandings, illustrate the contributions and highlight the differences between the existing methods.

It it correct that our approach is more efficient than SVD,
but it seems that reviewer may have misunderstood the connections/differences between the STOC paper (P. Jain et al. 2013) and our approach.
At the first glance the STOC paper looks directly applicable to our problem,
but the conditions of the paper and ours are quite different.
Specifically, the STOC paper requires a \textbf{Incoherent Matrix Assumption} for matrix completion,
which is not guaranteed to converge the global solution in our work.
Therefore, we disagree with reviewer that alternating minimization would reach a global solution with a simpler approach.
In addition, as shown in [41], the Riemannian manifold method converges faster than the alternating minimization approach.
%indicating that our approach is more capable of dealing with high-dimensional large scale data.

Apart from the misunderstanding, reviewer's concerns are mainly about the contributions given [10], [50] and (Liu et al. PAMI 2013).
Below, we brief the novelties and contribution over [10], [50] and (Liu et al. PAMI 2013).
%[10] and [50] formulate the fusion problem as a nuclear norm regularization problem, which cannot handle large-scale problems.
First, our method leverages $l_{1,2}$ norm for malicious classifier detection rather than the commonly used robust $l_{1}$ norm [10].
Second, we show the convergence of ALM for solving a non-convex problem rather than the convex problem in previous work (Liu et al. 2013).
Third, we propose to use matrix factorization (MF) technique to improve the efficiency comparing with nuclear norm based methods [10, 50].
Fourth, most MF methods only consider smooth $l_{2}$ loss, but we extend it to non-smooth $l_{1,2}$ loss.

Based on our discussions above,
Algorithm 2/3 should not be replaced by other methods based on the STOC paper.

Regarding the comments on Theorem 1, we clarify a few minor misunderstandings and technical issues.
First, the convergence of $\bX$ is guaranteed by [41].
Second, the proof of Theorem 1 relies on the gradient without the convexity requirement.
Third, the assumption for the boundedness of $\lambda_k$ is common (Th. Oh etal. TPAMI2016).
With $k \rightarrow \infty$, the gradient of $\calL$ vanishes.
Thus our algorithm converges and accumulation points will be achieved.

Thanks for the comments on empirical study.
However, reviewer may have overlooked important results from the tables.
Our method significantly outperforms LPBosst, as reported in Table 1 and 5.
Specifically, our method achieves much higher accuracy \textbf{(89.03\%)} than LPBoost \textbf{(86.24\%)} on UCF-101,
and CIFAR-100 \textbf{(77.72\% vs 76.59\%)}.

As indicated in Sec 4.4, we have provided very detailed approach for post-processing.
All the parameters of all algorithms are tuned by cross-validation with the same setting.
No human intervention was involved.
Therefore, the results should be reproducible and reliable.

It is the convention of CV papers to compare the results reported in recent papers on a standard setting.
CV researchers sometimes do not release their best model for business reasons,
but often share the not-that-new models with the community.
We show that combining a few weak models using our method,
the performance can be better than a single strong model.
To be more specific, the best single model on CIFAR-10 was reported in 12/2016 (see arXiv:1611.05431) with a test error of 3.58.
Our method fuse multiple single models which all perform worse than (arXiv:1611.05431), but can achieve low test error on CIFAR-10 (3.47 in Table 5).
This demonstrates the benefit of a good late fusion method.

We will take reviewer's comments seriously and will revise our paper carefully according to the comments.
We hope reviewer will find our paper contains novel ideas and acceptable for CVPR based on our explanations.

\noindent\emph{\textbf{To Assigned Reviewer 3}}

\textbf{Thanks for comments.}
Inappropriate figures, notations and typos will be revised/corrected.
$\ell_{1,2}$ loss preserves the fidelity within columns (lines 106-110),
and we will add more discussions and results of using $\ell_{2}$ norm.
Regarding the question on adversarial classifiers, we have discussed this issue in Sec4.1 \textbf{visualized in Fig.2.}
We will add more discussions and cite the related paper.
Thanks for the last suggestion, and it will be investigated in our future work.

\end{document}

### 2017-02-28 back-aaai/RLF_MF.tex
prepare for iccv

%\title{Consistent Late Fusion for Visual Recognition}
\title{Late Fusion via Subspace Search With Consistency Preservation}
%% Efficient

@@

\begin{figure}[h]
\centering\includegraphics[width=0.45\textwidth]{resource/frame_work.pdf}
\caption{Framework (example of $n=10, \calC=3, m=3$)}
\label{fig:framework}
\end{figure}

@@

\begin{small}
\begin{algorithm}[h!]

@@

\REQUIRE $\bL \in \dsR^{n \times m\calC}$, $p$ (the rank of $\bX$)
\ENSURE $\bX \in \dsR^{n \times m\calC}$
\STATE Initialize $\rho > 1$, $t = 0$, $\blambda_{0} = 0$, and $\mu_{0} > 0$.

@@

    %\STATE 1: Obtain $\bX^{(t)}$ by solving Problem~(\ref{eq:subproblem_wrt_X}) via LRGeomCG.
    \STATE 1: Obtain $\bX_{t}$ by solving Problem~(\ref{eq:subproblem_wrt_X}).

    %\STATE 2: Obtain $\bE^{(t)}$ by column-wise soft-thresholding~(\ref{eq:column_wise_soft_thresholding}).
    \STATE 2: Obtain $\bE_{t}$ by solving Problem~(\ref{eq:column_wise_soft_thresholding}).

@@

\end{algorithmic}
\caption{The ALM algorithm for Problem~(\ref{eq:mf_l21_constrained})}
\label{alg:alm_mf}
\end{algorithm}
\end{small}

@@

\begin{small}
\begin{algorithm}
  \begin{algorithmic}
    \REQUIRE $\bX = \U \diag(\sigma) \V^{\trsp} \in \M_{r}$, $\G$.

@@

    \STATE 3. $\U_{p} \leftarrow \bR_{v} - \U \bM$, $\V_{p} \leftarrow \bR_{u} - \V \bM^{\trsp}$.
  \end{algorithmic}
  \caption{Computation of $\grad f(\bX)$ (Algorithm 2 in~\cite{vandereycken2013lowrank})}
  \label{alg:compute_riemannian_grad}
\end{algorithm}
\end{small}

@@

\begin{small}
\begin{algorithm}
  \begin{algorithmic}
    \REQUIRE Initial $\bX_{1} \in \M_{r}$, tangent vector $\bfeta_{0} = \0$, $k = 1$.

@@

      \STATE 1. Compute Riemannian gradient $\bP_{k} = \grad f(\bX)$ by Algorithm~\ref{alg:compute_riemannian_grad}.

      \STATE 2. Compute a conjugate direction with PR+:
             $\bfeta_t = - \bP_{k} + \beta_{k} \mT_{\bX_{k-1} \rightarrow \bX_{k}}( \bfeta_{k-1}) \in T\M_{r}$.

      \STATE 3. Find a step size $t_{k}$ and set $\bX_{k} = R_{\bX_{t}}(t_{k} \bfeta_{k})$.

      \STATE 4. $k = k + 1$.

    \ENDWHILE
  \end{algorithmic}
  \caption{LRGeomCG (Algorithm 1 in~\cite{vandereycken2013lowrank})}
  \label{alg:LRGeomCG}
\end{algorithm}
\end{small}

@@

Similarly, to update $\bE$, we consider the augmented Lagrangian function \wrt. $\bE$ as below:
%\begin{align}\label{eq:subproblem_wrt_E_1}
%  \calL (\bE) = & || \bE ||_{1,2} + || \bL - \bX - \bE + \frac{\blambda}{\mu} ||_F^2 -\frac{1}{2\mu}|| \blambda ||_F^2  \nonumber \\
%              = & || \bE ||_{1,2} + || \bN - \bE ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
%\end{align}
{\small
\begin{align}\label{eq:subproblem_wrt_E_1}
  \calL (\bE) = & || \bE ||_{1,2} + || \bN - \bE ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
\end{align}
}
\noindent
where $\bN = \bL - \bX + \frac{\blambda}{\mu}$.
We thus obtain the subproblem \wrt. $\bE$ as below:
{\small
\begin{align}\label{eq:subproblem_wrt_E_2}
  \min_{\bE} & || \bE ||_{1,2} + || \bN - \bE ||_F^2 .
\end{align}
}
\noindent
The above problem can be efficiently solved by the following column-wise soft-thresholding operator~\cite{xiao2015FaLRR}:
{\small
\begin{align}\label{eq:column_wise_soft_thresholding}
  \bE_{i} = \calS_{\alpha}(\bY_{i}) = \left\{
    \begin{aligned}
      & \zerocolumn,~\text{if}~ ||\bN_{i}||_2 \leq \alpha   \\
      & \bY_{i} - \frac{\alpha \bY_{i}}{|| \bN_{i} ||_2},~\text{otherwise,}
    \end{aligned}
    \right.
\end{align}
}
\noindent
where $\bE_{i}$ and $\bN_{i}$ denote the $i$-th column of $\bE$ and $\bY$,
and $\alpha = \frac{2}{\mu}$.

\subsection{Post Process}
As we recover the low rank matrix $\bX$ from the label assignment matrix $\bL$,
it needs a post process to make the predicted label for each testing data.
Intuitively, there might be several possible ways to select as below:
\begin{itemize}
  \item $[AVE]$ A prediction score matrix $\bX^{*} \in \dsR^{n \times {\calC}}$ is obtained by averaging $[ \bX_1, \bX_2, ..., \bX_{\calC}]$.
		The indicator of the highest value in each row of $\bX^{*}$ is regard as the predicted label for the corresponding data.
  \item $[VOTE]$ For $\bX_j$ where $1 \leq j \leq m$, we set $\bI_{ij}$ is the index of the highest value in the $i$-th row of $\bX_j$.
  		Each $\bI_{ij}$ contributes one point to the $i$-th data with label $\bI_{ij}$.
  		Finally, we choose the label with the most votes to be the prediction results.
  \item $[GATE]$ $\bX_j$ where $1 \leq j \leq m$ are transformed through softmax function as a gate of the corresponding confidence score matrix, which is normalized by $L_2$ norm.
  		As $\bX_j$ contains outlier rejection information, we product the $\bX_j$ by the corresponding score matrix after softmax and normalization.
  		The similar process as the first strategy is applied to the above results, which predictes the final label.
\end{itemize}
According to the experiments, the last strategy outperforms than the others.
So We choose the last one as the post process for our fusion method and analyse inner reasons during experiment section.

@@

In this section, we first visualize the results of our approach on one synthetic dataset.
Then we evaluate the perfomance on eight publicly available real-world data sets,
UCF101~\cite{soomro2012ucf101}, CIFAR-10~\cite{krizhevsky2009learning}, CIFAR-100~\cite{krizhevsky2009learning}, Oxford-IIIT-Pet~\cite{parkhi2012cats}, PASCAL VOC 2007~\cite{pascal-voc-2007}, Oxford Flower 17~\cite{nilsback2006visual}, Pascal Sentence~\cite{rashtchian2010collecting} and Wikipedia~\cite{rasiwasia2010new}.
The strategy analysis for post process is detailed in the last subsection.

@@

\begin{table*}[t]
\small
\centering
\caption{Mean accuracy on real-world data sets.}
\begin{tabular}{c|c|c|c|c|c}
\hline
Method              & UCF-101          & CIFAR-10         & CIFAR-100        & Oxford-IIIT-Pet & PASCAL VOC 2007    \\\hline
ASF                 & 86.78\%          & 94.21\%          & 76.91\%          & 92.46\%         &   90.51\%          \\
MKL                 & 85.38\%          & 94.15\%          & 72.71\%          & 87.13\%         &   85.82\%          \\
RCEC                & 86.60\%          & 94.99\%          & 77.13\%          & 92.11\%         &   90.92\%          \\
FWOT                & -                & -                & -                & 92.90\%         &   91.20\%          \\
LPBoost             & 86.24\%          & 94.88\%          & 76.59\%          & 92.73\%         &   91.42\%          \\\hline
\textbf{Ours}       & \textbf{89.03\%} & \textbf{95.11\%} & \textbf{77.72\%} & \textbf{92.90\%}&   90.98\%          \\
\hline
\end{tabular}
\begin{tablenotes}
\footnotesize
\item[*]
  FWOT costs excessive time for training (\yanred{6 hours for a single run}), so we omit these results indicated by ``-''.
\end{tablenotes}
\label{table:total_acc}
\end{table*}

\begin{table*}[t]
\small
\centering
\caption{Experimental results on real-world data sets. Computational time is recorded in seconds.}
\begin{tabular}{c|c|c|c|c|c}
\hline
Method              & UCF-101    & CIFAR-10  & CIFAR-100  & Oxford-IIIT-Pet & PASCAL VOC 2007 \\\hline
RCEC                & 86.60      & 81.41     &  255.51    & 18.82           &   16.45         \\
FWOT                & $\infty$   & $\infty$  & $\infty$   & 61697           &   19674         \\
LPBoost             & 110.81     & 72.45     &  4750.9    & 43.67           &   7.46          \\\hline
Ours                & 421.23     & 5.384     &  417.26    & 76.16           &   16.21         \\
\hline
\end{tabular}
\begin{tablenotes}
\footnotesize
\item[*]
  FWOT costs excessive time for training (\yanred{6 hours for a single run}), so we omit these results indicated by ``$\infty$''.
\end{tablenotes}
\label{table:total_time}
\end{table*}

@@

In this section, we introduce the details about our experiments on each data set,
and demonstrate the empirical results in Table~\ref{table:total_acc} and Table~\ref{table:total_time}.
Five data sets are used to compare the performance on each contrast algorithm, including UCF-101, CIFAR-10, CIFAR-100, Oxford-III-Pet and PASCAL VOC 2007.
`-' means the contrast algorithm does not work due to heavy memory or time consumption,
and `$\infty$' means it will take more than one day to complete the corresponding method.
The computational cost of cross-validation is not counted in FWOT and LPBoost.

@@

@@

As we have 50000 training data and 10000 testing data,
FWOT algorithm has one step to deal with $n\times n$ matrixes, which are excessive to train~(more than one day).
LPBoost algorithm needs to create a $nm\times \calC$ constraint matrix linear programming solvers\footnote{The author use the MOSEK interior-point solver, see www.mosek.com.},
which occupies too much memory and still consumes long time to train, so we solve this problem by using sparse matrix storage and parallel during matlab.
We also use `-s 2' parameters in liblinear to speedup training process.
Results of total six competing algorithms are shown in Table~\ref{table:total_acc} and \ref{table:total_time}.

@@

CIFAR-100 is similar with CIFAR-10, except it has 100 classes containing 600 images each.
There are 50000 training data and 10000 testing data as CIFAR-10.
Twelve CNN features used in this experiment are described in the feature selection section.
Training and comparison process are the same as CIFAR-10.

@@

\begin{table}[h]
\small
\centering
\caption{Mean Accuracy with Different Strategies}
\begin{tabular}{c|c|c|c}
\hline
Strategy            & Wikipedia & Flowers 17 & Pascal Sentence \\\hline
[AVE]               & 47.78\%   & 96.77\%    &   66.40\%       \\\hline
[VOTE]              & 47.85\%   & 96.61\%    &   66.20\%       \\\hline
[GATE]              & 49.03\%   & 96.77\%    &   67.20\%       \\
\hline
\end{tabular}
\label{table:strategy}
\end{table}

>>>>

%\title{Consistent Late Fusion for Visual Recognition}
\title{Late Fusion via Subspace Search with Consistency Preservation}
%% Efficient

@@

\begin{figure}[ht]
\centering\includegraphics[width=0.45\textwidth]{resource/frame_work.pdf}
\caption{Framework (example of $n=10, \calC=3, m=3$)}
\label{fig:framework}
\end{figure}

@@

%\begin{small}
\begin{algorithm}[ht]

@@

\REQUIRE $\bL \in \dsR^{n \times m\calC}$, rank($\bX$) = $p$

\STATE Initialize $\rho > 1$, $t = 0$, $\blambda_{0} = 0$, $\bE_{0} = 0$, and $\mu_{0} > 0$.

@@

    %\STATE 1: Obtain $\bX^{(t)}$ by solving Problem~(\ref{eq:subproblem_wrt_X}) via LRGeomCG.
    \STATE 1: Obtain $\bX_{t+1}$ by solving Problem~(\ref{eq:subproblem_wrt_X}).

    %\STATE 2: Obtain $\bE^{(t)}$ by column-wise soft-thresholding~(\ref{eq:column_wise_soft_thresholding}).
    \STATE 2: Obtain $\bE_{t+1}$ by solving Problem~(\ref{eq:column_wise_soft_thresholding}).

@@

\ENSURE $\bX \in \dsR^{n \times m\calC}$

\end{algorithmic}
\caption{The ALM algorithm for Problem~(\ref{eq:mf_l21_constrained})}
\label{alg:alm_mf}
\end{algorithm}
%\end{small}

@@

%\begin{small}
\begin{algorithm}
  \begin{algorithmic}
    \REQUIRE $\bX = \U \diag(\sigma) \V^{\trsp} \in \M_{r}$, $\G$.

@@

    \STATE 3. $\U_{p} \leftarrow \bR_{v} - \U \bM$, $\V_{p} \leftarrow \bR_{u} - \V \bM^{\trsp}$.

  \end{algorithmic}
  \caption{Computation of $\grad f(\bX)$ (Algorithm 2 in~\cite{vandereycken2013lowrank})}
  \label{alg:compute_riemannian_grad}
\end{algorithm}
%\end{small}

@@

%\begin{small}
\begin{algorithm}
  \begin{algorithmic}
    \REQUIRE Initial $\bX_{1} \in \M_{r}$, tangent vector $\bfeta_{0} = \0$, $k = 1$.

@@

      \STATE 1. Compute Riemannian gradient $\bP_{k} = \grad f(\bX_{k})$ by Algorithm~\ref{alg:compute_riemannian_grad}.

      \STATE 2. Compute a conjugate direction with PR+:
             $\bfeta_k = - \bP_{k} + \beta_{k} \mT_{\bX_{k-1} \rightarrow \bX_{k}}( \bfeta_{k-1}) \in T\M_{r}$.

      \STATE 3. Find a step size $t_{k} = \min_{t} f(\bX + t\bfeta_{k}) $

      \STATE 4. Update $\bX_{k+1} = R_{\bX_{k}}(t_{k} \bfeta_{k})$.

      \STATE 5. $k = k + 1$.

    \ENSURE $\bX \in \M_{r}$.

  \end{algorithmic}
  \caption{LRGeomCG (Algorithm 1 in~\cite{vandereycken2013lowrank})}
  \label{alg:LRGeomCG}
\end{algorithm}
%\end{small}

@@

Similarly, to update $\bE$, we consider the augmented Lagrangian function \wrt. $\bE$ as below:
%\begin{align}\label{eq:subproblem_wrt_E_1}
%  \calL (\bE) = & || \bE ||_{1,2} + || \bL - \bX - \bE + \frac{\blambda}{\mu} ||_F^2 -\frac{1}{2\mu}|| \blambda ||_F^2  \nonumber \\
%              = & || \bE ||_{1,2} + || \bN - \bE ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
%\end{align}
{\small
\begin{align}\label{eq:subproblem_wrt_E_1}
  \calL (\bE) = & || \bE ||_{1,2} + || \bN - \bE ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
\end{align}
}
\noindent
where $\bN = \bL - \bX + \frac{\blambda}{\mu}$.
We thus obtain the subproblem \wrt. $\bE$ as below:
{\small
\begin{align}\label{eq:subproblem_wrt_E_2}
  \min_{\bE} & || \bE ||_{1,2} + || \bN - \bE ||_F^2 .
\end{align}
}
\noindent
The above problem can be efficiently solved by the following column-wise soft-thresholding operator~\cite{xiao2015FaLRR}:
{\small
\begin{align}\label{eq:column_wise_soft_thresholding}
  \bE_{i} = \calS_{\alpha}(\bN_{i}) = \left\{
    \begin{aligned}
      & \zerocolumn,~\text{if}~ ||\bN_{i}||_2 \leq \alpha   \\
      & \bN_{i} - \frac{\alpha \bN_{i}}{|| \bN_{i} ||_2},~\text{otherwise,}
    \end{aligned}
    \right.
\end{align}
}
\noindent
where $\bE_{i}$ and $\bN_{i}$ denote the $i$-th column of $\bE$ and $\bN$,
%and $\alpha = \frac{2}{\mu}$.
and $\alpha = \frac{1}{2}$.

\subsection{Post Process}
As we recover the low rank matrix $\bX$ from the label assignment matrix $\bL$,
it needs a post process to generate the prediction label for each testing data.
Intuitively, there might be several possible ways to select as below:
\begin{itemize}
  \item $[AVE]$ A prediction score matrix $\bX^{*} \in \dsR^{n \times {\calC}}$ is obtained by averaging $[ \bX_1, \bX_2, ..., \bX_{\calC}]$.
		The indicator of the highest value in each row of $\bX^{*}$ is regard as the predicted label for the corresponding data.
  \item $[VOTE]$ For $\bX_j$ where $1 \leq j \leq m$, we set $\bI_{ij}$ as the index of the highest value in the $i$-th row of $\bX_j$.
  		Each $\bI_{ij}$ contributes one point to the $i$-th data with label $\bI_{ij}$.
  		Finally, we choose the label with the most votes to be the prediction results.
  \item $[GATE]$ $\bX_j$ where $1 \leq j \leq m$ are transformed through softmax function as a gate of the corresponding confidence score matrix, which is normalized by $L_2$ norm.
  		As $\bX_j$ contains outlier rejection information, we product the $\bX_j$ by the corresponding score matrix after softmax and normalization.
  		The similar process as the first strategy is applied to the above results, which predictes the final labels.
\end{itemize}
According to the experiments, the last strategy ``GATE'' outperforms than the others.
So We choose the last one as the post process for our fusion method and analyse inner reasons during the experiment section.

@@

In this section, we first visualize the results of our approach on the synthetic dataset.
Then we evaluate the perfomance on eight publicly available real-world data sets,
UCF101~\cite{soomro2012ucf101}, CIFAR-10~\cite{krizhevsky2009learning}, CIFAR-100~\cite{krizhevsky2009learning}, Oxford-IIIT-Pet~\cite{parkhi2012cats}, PASCAL VOC 2007~\cite{pascal-voc-2007}, Oxford Flower 17~\cite{nilsback2006visual}, Pascal Sentence~\cite{rashtchian2010collecting} and Wikipedia~\cite{rasiwasia2010new}.
The strategy analysis for post process is detailed in the last subsection.

@@

@@

In this section, we introduce the details about our experiments on each data set,
and demonstrate the empirical results in Table~\ref{table:total_acc} and Table~\ref{table:total_time}.
Five data sets are used to compare the performance on each contrast algorithm, including UCF-101, CIFAR-10, CIFAR-100, Oxford-III-Pet and PASCAL VOC 2007.
And the computational cost of cross-validation is not counted in FWOT and LPBoost.

@@

\begin{table*}[t]
\small
\centering
\caption{Mean accuracy on real-world data sets.}
\begin{tabular}{c|c|c|c|c|c}
\hline
Method              & UCF-101          & CIFAR-10         & CIFAR-100        & Oxford-IIIT-Pet & PASCAL VOC 2007    \\\hline
ASF                 & 86.78\%          & 94.21\%          & 76.91\%          & 92.46\%         &   90.51\%          \\
MKL                 & 85.38\%          & 94.15\%          & 72.71\%          & 87.13\%         &   85.82\%          \\
RCEC                & 86.60\%          & 94.99\%          & 77.13\%          & 92.11\%         &   90.92\%          \\
FWOT                & -                & -                & -                & 92.90\%         &   91.20\%          \\
LPBoost             & 86.24\%          & 94.88\%          & 76.59\%          & 92.73\%         &   91.42\%          \\\hline
\textbf{Ours}       & \textbf{89.03\%} & \textbf{95.11\%} & \textbf{77.72\%} & \textbf{92.90\%}&   90.98\%          \\
\hline
\end{tabular}
\begin{tablenotes}
\footnotesize
\item[*]
  FWOT costs excessive time for training UCF-101, CIFAR-10 , CIFAR-100~(over 24 hours), so we omit these results indicated by ``-''.
\end{tablenotes}
\label{table:total_acc}
\end{table*}

\begin{table*}[t]
\small
\centering
\caption{Experimental results on real-world data sets. Computational time is recorded in seconds.}
\begin{tabular}{c|c|c|c|c|c}
\hline
Method              & UCF-101    & CIFAR-10  & CIFAR-100  & Oxford-IIIT-Pet & PASCAL VOC 2007 \\\hline
RCEC                & 86.60      & 81.41     &  255.51    & 18.82           &   16.45         \\
FWOT                & $\infty$   & $\infty$  &  $\infty$     & 61697           &   19674         \\
LPBoost             & 110.81     & 72.45     &  4750.9    & 43.67           &   7.46          \\\hline
Ours                & 421.23     & 5.384     &  417.26    & 76.16           &   16.21         \\
\hline
\end{tabular}
\begin{tablenotes}
\footnotesize
\item[*]
  FWOT costs excessive time for training UCF-101, CIFAR-10 , CIFAR-100~(over 24 hours), so we omit these results indicated by ``$\infty$''.
\end{tablenotes}
\label{table:total_time}
\end{table*}

@@

As we have 50000 training data and 10000 testing data,
FWOT algorithm has one step to deal with $n\times n$ matrixes, which are excessive to train~(more than one day).
LPBoost algorithm needs to create a $(n\calC - n) \times (1 + n + m)$ constraint matrix linear programming solvers
\footnote{\cite{gehler2009feature} use the MOSEK interior-point solver, see www.mosek.com.},
which occupies too much memory and still consumes long time to train, so we solve this problem by using sparse matrix storage and parallel during matlab.
We also use `-s 2' parameters in liblinear to speedup training process.
Results of total six contrast algorithms are shown in Table~\ref{table:total_acc} and \ref{table:total_time}.

@@

CIFAR-100 is similar with CIFAR-10, except it has 100 classes containing 600 images each.
There are 50000 training data and 10000 testing data as CIFAR-10.
Twelve CNN features used in this experiment are described in the feature selection section.
Training and comparison process are the same as CIFAR-10.
Detailed results are shown in Table~\ref{table:total_acc} and \ref{table:total_time}.

@@

\begin{table}[ht]
%\small
\centering
\caption{Mean Accuracy with Different Strategies}
\begin{tabular}{c|c|c|c}
\hline
Strategy            & Wikipedia         & Flowers 17          & Pascal Sentence     \\\hline
[AVE]               & 47.78\%           & \textbf{96.77\%}    & 66.40\%             \\\hline
[VOTE]              & 47.85\%           & 96.61\%             & 66.20\%             \\\hline
[GATE]              & \textbf{49.03\%}  & \textbf{96.77\%}    & \textbf{67.20\%}    \\
\hline
\end{tabular}
\label{table:strategy}
\end{table}
